Supplementary Content

### 2022-03-29 experiments/2_supplement/supplement.Rmd

The counter-intuitive effect of diversity in the phototrophic sulfur bacteria (PB) possibly results from their positive effects on the oxic state. The phototrophic sulfur bacteria oxidise reduced sulfur to oxidised sulfur. Since reduced sulfur inhibits the cyanobacteria (CB), PB can have a positive effect on CB via their consumption of reduced sulfur Hence, high growth rates of PB will have a positive effect on CB, and therefore favour the oxic state. We would expect to see that higher diversity of PB is associated with lower concentrations of reduced sulfur and higher concentrations of oxidised sulfur before the transition.

@@

dd %>%
  filter(State_variable %in% c("O", "SR", "SO"),
         direction == "up",
         a_O < as.numeric(aO_flip_sim2),
         a_O > -3.5) %>%
  ggplot(aes(x = log10(Quantity_sim1),
                 y = log10(Quantity_sim2),
                 col = a_O )) +
  geom_point(lwd = 3) +
  geom_path() +
  scale_color_gradient(low = "yellow", high = "red", na.value = NA,
                       breaks = labs,
                       labels = labs) +
  #coord_trans(x = "log10", y = "log10") +
  facet_wrap( ~ State_variable, scales = "free") +
  geom_abline(intercept = 0, slope = 1) +
  xlab("Log10(Concentration)\nLow PB diversity") +
  ylab("Log10(Concentration)\nHigh PB diversity") +
  labs(col="Log10(Oxygen diffusivity)") +
  theme_bw() +
  theme(legend.position="top")

>>>>

The counter-intuitive effect of diversity in the phototrophic sulfur bacteria (PB) possibly results from their positive effects on the oxic state. The phototrophic sulfur bacteria oxidise reduced sulfur to oxidised sulfur. Since reduced sulfur inhibits the cyanobacteria (CB), PB can have a positive effect on CB via their consumption of reduced sulfur. Hence, high growth rates of PB will have a positive effect on CB, and therefore favour the oxic state. We would expect to see that higher diversity of PB is associated with lower concentrations of reduced sulfur and higher concentrations of oxidised sulfur before the transition.

@@

dd %>%
  filter(State_variable %in% c("O", "SR", "SO"),
         direction == "up",
         a_O < as.numeric(aO_flip_sim2),
         a_O > -3.5) %>%
  ggplot(aes(x = log10(Quantity_sim1),
                 y = log10(Quantity_sim2),
                 col = a_O )) +
  geom_point(lwd = 3) +
  geom_path() +
  scale_color_gradient(low = "yellow", high = "red", na.value = NA,
                       breaks = labs,
                       labels = labs) +
  #coord_trans(x = "log10", y = "log10") +
  facet_wrap( ~ State_variable, scales = "free") +
  geom_abline(intercept = 0, slope = 1) +
  xlab("log10(concentration) (µM)\nLow PB diversity") +
  ylab("log10(concentration) (µM)\nHigh PB diversity") +
  labs(col=expression(paste("log"[10],"(oxygen diffusivity) (h"^{-1}, ")"))) +
  theme_bw() +
  theme(legend.position="top")
